---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      fig.path = "README-")
```


## Installation
```{r, echo = TRUE, eval = FALSE}
devtools::install_github(repo = "anthonypileggi/gradeR")
```

## Introduction
The `gradeR` package was originally designed for teachers that are incorporating Swirl in their lesson plans and want an easy way to track student progress.  Functionally, it is a simple tool that compares two workspaces.

## Workflow: Grading Swirl Assignments

#### Teacher

1. Create a new folder & move into it:
        ```r
            dir.create("Lesson1")
           setwd(file.path(getwd(), "Lesson1"))
        ```
2. Complete the desired Swirl lesson.
3. Create the answer key: `gradeR::createKey("Lesson1")` ("_KEY.Rdata" will be appended to the name)
4. Store all student submissions (.Rdata) in this folder
5. Grade the assignments: `gradeR::grade()`

#### Student

1. Clear the current working directory: `rm(list = ls())`
2. Complete the Swirl lesson.
3. Save (& submit) your workspace: `save.image("Lesson1_anthony.Rdata")`
