---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      fig.path = "README-")
```


## Installation
```{r, echo = TRUE, eval = FALSE}
devtools::install_github(repo = "anthonypileggi/gradeR")
```

## Introduction
The `gradeR` package was originally designed for teachers that are incorporating Swirl in their lesson plans and want an easy way to track student progress.  Functionally, it is a simple tool that compares two workspaces.

## Workflow: Grading Swirl Assignments

#### Create an Answer Key
1. Create a new folder & move into it: `dir.create("Lesson1"); setwd(file.path(getwd(), "Lesson1"))`
2. Complete the desired Swirl lesson.
3. Create the answer key: `gradeR::createKey("Lesson1")` ("_KEY.Rdata" will be appended to the name)


#### Instructions for Students
1. Clear the current working directory: `rm(list = ls())`
2. Complete the Swirl lesson.
3. Save (& submit) your workspace: `save.image("Lesson1_anthony.Rdata")`


#### Grade the Assignments
1. Collect all student submissions (.Rdata) within the folder containing the answer key.
2. Set that folder as the current working directory: `setwd(file.path(getwd(), "Lesson1"))` 
2. Identify the answer key: `id_key <- grepl("_KEY", list.files())`
3. Grade the assignments: `gradeR::grade(list.files()[!id_key], list.files()[id_key])`

